### 2015-06-08 Manuscript/Missing_mammals-draft.tex
Error in counts

The number of living mammalian taxa with no available cladistic data was surprisingly high at the species-level: only @24 out of @28 orders have a high coverage of taxa with available cladistic data (and two of the 28 orders are monospecific!). % NC: Bit odd to say it's suprisingly high then say there are lots of orders with "high" coverage. I've added an "only" but 24 of 28 sounds quite good to me...
This high coverage threshold of 75\% of taxa with available cladistic data represents the minimum amount of data required before missing data has a significant effect on the topology of Total Evidence trees \citep{GuillermeCooper}.
Beyond this threshold, there is considerable displacement of wildcard taxa (\textit{sensu} \citep{kearneyfragmentary2002}) and decreases in clade conservation \citep{GuillermeCooper}.
Therefore we expect a high probability of topological artefacts for the placement of fossil taxa at the species-level in most mammalian orders.
However, data coverage seems to be less of an issue at higher taxonomic levels (i.e. genus- and family-level).
This point is important from a practical point of view because of the slight discrepancy between the neontological and palaeontological concept of species.
While neontological species are described using morphology, genetic distance, spatial distribution and even behaviour \citep[e.g.][]{kellymolecular2014}, palaeontological data can be based only on morphological, spatial and temporal data \citep[e.g.][]{ni2013oldest}.
Because of this difference between neontological species (i.e. reproductive isolates) and paleontological species (i.e. morpho-species), most palaeontological studies are using the genus-level as their smallest OTU \citep[e.g.][]{ni2013oldest,O'Leary08022013}.
Thus data availability at the genus-level in living mammals should be our primary concern when aiming to build phylogenies of living and fossil taxa.

>>>>

The number of living mammalian taxa with no available cladistic data was surprisingly high at the species-level: only @4 out of @28 orders have a high coverage of taxa with available cladistic data (and two of the 28 orders are monospecific!).
This high coverage threshold of 75\% of taxa with available cladistic data represents the minimum amount of data required before missing data has a significant effect on the topology of Total Evidence trees \citep{GuillermeCooper}.
Beyond this threshold, there is considerable displacement of wildcard taxa (\textit{sensu} \citep{kearneyfragmentary2002}) and decreases in clade conservation \citep{GuillermeCooper}.
Therefore we expect a high probability of topological artefacts for the placement of fossil taxa at the species-level in most mammalian orders.
However, data coverage seems to be less of an issue at higher taxonomic levels (i.e. genus- and family-level).
This point is important from a practical point of view because of the slight discrepancy between the neontological and palaeontological concept of species.
While neontological species are described using morphology, genetic distance, spatial distribution and even behaviour \citep[e.g.][]{kellymolecular2014}, palaeontological data can be based only on morphological, spatial and temporal data \citep[e.g.][]{ni2013oldest}.
Because of this difference between neontological species (i.e. reproductive isolates) and paleontological species (i.e. morpho-species), most palaeontological studies are using the genus-level as their smallest OTU \citep[e.g.][]{ni2013oldest,O'Leary08022013}.
Thus data availability at the genus-level in living mammals should be our primary concern when aiming to build phylogenies of living and fossil taxa.
